---
title: "Project 2"
author: "Brandy Carr"
format: 
  html:
    self-contained: true
    echo: true
    message: false
    warning: false
    error: true # IMPORTANT NOTE - this makes the file render even if there is an error. it is imperative that you check your .html document *before submission* to make sure that it has all results in it.
editor: source
---

**This week you angain analyze data from the Jackson Heart Study (JHS). You can find the data on Canvas, in the Week 1 module. For full credit, you must include all code chunks and R output backing up your responses.**

**0. Import the JHS data.**

```{r}
JHS <- haven::read_sas("analysis1.sas7bdat")
#DT::datatable(head(JHS, n=10), filter="top") # first 10 rows of data
```

**1a. Model systolic blood pressure (*sbp*; mmHg) as a function of age (*age*; years), education (*HSgrad*; 0=no, 1=yes), and body mass index (*BMI*; kg/m<sup>2</sup>), and the following interactions: body mass index $\times$ age and body mass index $\times$ education. Remember to report the resulting model.**

```{r}
library(tidyverse)
JHS1 <- JHS %>% select(sbp, age, HSgrad, BMI) %>% na.omit()
m1 <- glm(sbp ~ HSgrad + BMI + age + BMI * (age + HSgrad), data=JHS1, family="gaussian")
summary(m1)
```

**1b. Perform the appropriate hypothesis test to determine if the interaction between body mass index and age is significant. Test at the $\alpha=0.05$ level. Remember to typeset your results.**

```{r}

```

**1c. Perform the appropriate hypothesis test to determine if the interaction between body mass index and education is significant Test at the $\alpha=0.05$ level. Remember to typeset your results.**

```{r}

```

**1d. Create the following models (i.e., plug in the following values and algebraically simplify): (1) body mass index of 32, (2) body mass index of 27, and (3) body mass index of 25.  Remember to report the resulting models. **

<!-- this does not require R code - I am asking you to simplify the models to get rid of the interaction term -->

**1e. Provide brief interpretations for the slopes of the predictors for the one of the models in 1d (your choice, but make sure you specify which model you are interpreting).**

**1f. Construct an appropriate data visualization to help with explaining the model results. Systolic blood pressure should be on the *y*-axis, age should be on the *x*-axis, and use the regression lines constructed in 1d.**

```{r}

```

**1g. Graphically assess the assumptions implied by used the normal distribution. Remember to draw your overall conclusion with appropriate written justification.**

```{r}

```

**2a. Model systolic blood pressure (*sbp*; mmHg) as a function of age (*age*; years), education (*HSgrad*; 0=no, 1=yes), and health status as defined by body mass index (*BMI3cat*; 0=poor health, 1=intermediate health, 2=ideal health), and the following interactions: health status as defined by body mass index $\times$ age and health status as defined by body mass index $\times$ education. Remember to report the resulting model.**

```{r}

```

**2b. Perform the appropriate hypothesis test to determine if the interaction between health status as defined by body mass index and age is significant. Test at the $\alpha=0.05$ level. Remember to typeset your results**

```{r}

```

**2c. Perform the appropriate hypothesis test to determine if the interaction between health status as defined by body mass index and education is significant. Test at the $\alpha=0.05$ level. Remember to typeset your results.**

```{r}

```

**2d. Create the following models (i.e., plug in the following values and algebraically simplify): (1) poor health (bmi3cat = 0), (2) intermediate health (bmi3cat = 1), and (3) ideal health (bmi3cat = 2).  Remember to report the resulting models.**



**2e. Provide brief interpretations for the slopes of the predictors from one of the models in 2d (your choice).**



**2f. Construct an appropriate data visualization to help with explaining the model results. Systolic blood pressure should be on the *y*-axis, age should be on the *x*-axis, and use the regression lines constructed in 2d.**

```{r}

```

**2g. Graphically assess the assumptions implied by used the normal distribution. Remember to draw your overall conclusion with appropriate written justification.**

```{r}

```

**3. Required for graduate students / extra credit for undergraduate students: Write a paragraph to summarize the above analysis, written such that a non-quantitative person could understand. Include if you recommend using BMI as a continuous variable or a categorical variable. For full credit, you must explain your reasoning.**


