---
title: "STA6232: Project 2"
author: "Brandy Carr"
date: "1/22/2024"
output:
  rmdformats::material:
    thumbnails: false
    gallery: true
    fig_width: 5
    fig_height: 3
pkgdown:
  as_is: true
---

**2a. Model systolic blood pressure (*sbp*; mmHg) as a function of age (*age*; years), education (*HSgrad*; 0=no, 1=yes), and health status as defined by body mass index (*BMI3cat*; 0=poor health, 1=intermediate health, 2=ideal health), and the following interactions: health status as defined by body mass index $\times$ age and health status as defined by body mass index $\times$ education. Remember to report the resulting model.**

```{r}

```

**2b. Perform the appropriate hypothesis test to determine if the interaction between health status as defined by body mass index and age is significant. Test at the $\alpha=0.05$ level. Remember to typeset your results**

```{r}

```

**2c. Perform the appropriate hypothesis test to determine if the interaction between health status as defined by body mass index and education is significant. Test at the $\alpha=0.05$ level. Remember to typeset your results.**

```{r}

```

**2d. Create the following models (i.e., plug in the following values and algebraically simplify): (1) poor health (bmi3cat = 0), (2) intermediate health (bmi3cat = 1), and (3) ideal health (bmi3cat = 2).  Remember to report the resulting models.**



**2e. Provide brief interpretations for the slopes of the predictors from one of the models in 2d (your choice).**



**2f. Construct an appropriate data visualization to help with explaining the model results. Systolic blood pressure should be on the *y*-axis, age should be on the *x*-axis, and use the regression lines constructed in 2d.**

```{r}

```

**2g. Graphically assess the assumptions implied by used the normal distribution. Remember to draw your overall conclusion with appropriate written justification.**

```{r}

```

**3. Required for graduate students / extra credit for undergraduate students: Write a paragraph to summarize the above analysis, written such that a non-quantitative person could understand. Include if you recommend using BMI as a continuous variable or a categorical variable. For full credit, you must explain your reasoning.**

-->
